\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
		\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{\small#3} & \textit{\small #4} \\
		\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\Large Ryan Hassing & Email : ryan.howardanton.hassing@gmail.com \\
	& Phone : 6103087776 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Drexel University}{Philadelphia, PA}
			{B.S. Computer Science \& B.S. Mathematics}{Aug. 2015 -- June 2020}
	\resumeSubHeadingListEnd

%--------Coursework-----------
\section{Coursework}
	\textbf{Mathematics:} Modern Analysis I \& II, Numerical Analysis I \& II, Probability \& Statistics I \& II, Abstract Algebra I \& II, Combinatorics, Partial Differential Equations, Complex Variables, Intro to Optimization Theory \\
	\textbf{Computer Science:} Advanced Programming Techniques, Data Structures, Web \& Mobile App Development, Systems Programming, Systems Architecture, Software Design, Programming Language Concepts, Machine Learning, Software Engineering, Introduction to Parallel Computer Architecture

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
	\textbf{Languages:} Python, Matlab, C, C++, CUDA, Javascript, Java, Go, Bash\\
	\textbf{Tools:} pthreads, OpenMP, numpy, Flask, OpenCV, mySQL, SQLite, MongoDB\\

%-----------EXPERIENCE-----------------
\section{Experience}
	\resumeSubHeadingListStart

		\resumeSubheading
			{Senior Design}{Drexel University, Philadelphia, PA}
			{Project Manager, Software Developer}{Sept 2019 - June 2020}
		\begin{itemize}
			\item\small{Worked with a team of 7 to develop GUI application and system backend for IoT device data collection and processing.}
			\item\small{Effectively communicated project scope and schedule with advisors.}
			\item\small{Directed team through requirements gathering, design, development, and testing phases.}
			\item\small{Investigated and identified requirements via stakeholder interviews and communication with subject matter experts, documented in software requirements specification.}
			\item\small{Designed modular software system to satisfy requirements, documented in software design document.}
			\item\small{Developed Python-based database interface module to transfer IoT device data to and from multiple database systems.}
			\item\small{Developed Python-based API to process requests to system backend.}
		\end{itemize}

		\resumeSubheading
			{Drexel University College of Medicine}{Department of Pathology \& Laboratory Medicine}
			{Research Assistant}{April 2018 - Sept 2018}
		\begin{itemize}
			\item\small{Performed analysis of breast cancer slides using computer vision tools.}
			\item\small{Automated tests on large samples of data (1000+ images).}
			\item\small{Used artificial intelligence algorithms to develop predictive models for cancer outcomes.}
		\end{itemize}

		\resumeSubheading
			{Brandywine Global Investment Management}{Philadelphia, PA}
			{Software Developer}{April 2017 - Sept 2017}
		\begin{itemize}
			\item\small{Developed Python scripts to track business processes at the firm, including:}
			\begin{itemize}
				\item\small{Compiling documentation for 1400 batch jobs from multiple sources,}
				\item\small{Identifying and documenting modifications of batch jobs,}
				\item\small{Reporting on success of batch jobs.}
			\end{itemize}
			\item\small{Developed code that interfaced with large datasets in Excel and SQL.}
		\end{itemize}

		\resumeSubheading
			{Freshman Design}{Drexel University, Philadelphia, PA}
			{Software Designer \& Developer}{January 2016 - June 2016}
		\begin{itemize}
			\item\small{Developed machine vision program capable of detecting building windows.}
			\item\small{Implemented machine vision algorithms using OpenCV library.}
			\item\small{Interfaced hardware and software using Raspberry Pi, camera, ultrasonic, and LiDAR sensors.}
		\end{itemize}
	\resumeSubHeadingListEnd

\end{document}
